Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-08-11 writing/embedded_meta_learning_main.tex
Minor tweaks to related lit, following up on reviews

Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}, and meta-learning \citep[e.g.]{Li2019a, Rusu2019}. Our work is also related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017} and continual learning \citep[e.g.]{Hu2019}. It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}. In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture. Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general. \par 

>>>>

Our architecture builds directly off of prior work on HyperNetworks \citep{Ha2016} -- networks which parameterize other networks -- and other recent applications thereof, such as guessing parameters for a model to accelerate model search \citep[e.g.][]{Brock2018a, Zhang2019}, and meta-learning \citep[e.g.]{Li2019a, Rusu2019}. Our work is also related to the longer history of work on different time-scales of weight adaptation \citep{Hinton1982, Kumaran2016} that has more recently been applied to meta-learning contexts \citep[e.g.][]{Ba2016, Munkhdalai2017, Garnelo2018} and continual learning \citep[e.g.]{Hu2019}. It is more abstractly related to work on learning to propose architectures \citep[e.g.][]{Zoph2016, Cao2019}, and to models that learn to select and compose skills to apply to new tasks \citep[e.g.][]{Andreas, Andreas2016, Tessler2016, Reed2015, Chang2019a}. In particular, some of the work in domains like visual question answering has explicitly explored the idea of building a classifier conditioned on a question \citep{Andreas, Andreasa}, which is related to one of the possible computational paths through our architecture. Work in model-based reinforcement learning has also partly addressed how to transfer knowledge between different reward functions \citep[e.g.][]{Laroche2017}; our approach is more general. Indeed, our insights could be combined with model-based approaches, for example our approach could be used to adapt a task embedding, which would then be fed to a learned planning model to execute that behavior.\par 
